Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-28 Docs/IJES/journal.tex
[C-5] The term TipH and Hmax is used in Figure5 but is not declared. Figure 5 uses “Populate”, but actually it is assignment of decision variables. The pseudocode in Figure 5 is extremely inconsistent. It is very hard to follow what each step of the algorithm is achieving. For the three multi-core version of ESBMC, the author must comment on the complexity of ESBMC-SS, ESBMC-PS, ESBMC-PB. Also, the Open-MP overhead must be described for each version of these algorithms.

Algorithm of Figure~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances. The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$). While the step is being executed, the controller checks whether this step is still needed (line $4$); otherwise, the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.  \textcolor{blue}{It is worth mentioning that there is no interchange communication among the workers, but they are responsible to notify the controller if a violation is found.}

@@

>>>>

Algorithm of Figure~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances. The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$). While the step is being executed, the controller checks whether this step is still needed (line $4$); otherwise, the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.  \textcolor{blue}{Note that there is no interchange communication among workers, but they are responsible for notifying the controller if a given violation is found.}

@@

%----------------------------------------------
\subsection{\textcolor{blue}{Time Complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB}}
\label{complexity}
%----------------------------------------------

\textcolor{blue}{With respect to the time complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB algorithms, they can all be described in two parts, which include the parallelism and the optimization solving. In the first part, the ESBMC-SS, ESBMC-PS, and ESBMC-PB time complexity is considered to be linear ({\it i.e.}, they are denoted by $O(n)$), taking into account a sequential time since each algorithm runs all possible solutions at once. However, each execution instance of ESBMC-SS, ESBMC-PS, and ESBMC-PB solves a specific optimization problem that is considered to be NP-Hard, as described by~\cite{Arato2003}. Thus, even a parallel execution being implemented, including (possible) overheads due to the use of the OpenMP library, the time complexity of ESBMC-SS, ESBMC-PS, and ESBMC-PB is still NP-Hard.}
